troubleshooting

### 2024-04-18 README.Rmd
updated n term and cterm cleavage functions to allow for user to specify n of AA to the side of cleavage event. Also updated docs and down stream functions.
A couple of other minor things in here too

Sequences are presented as the 4 amino acids on both sides of a cleavage. X indicates that there was nothing on that side in the library because it was cleaved close to the edge.

```{r}
cleavage_added_data = add_cleavages(joined_with_library)

>>>>

Sequences are presented as the user specified number of amino acids on both sides of a cleavage. The default is 4, but there is interest in looking at motifs that are farther away from the cut site. Note that X indicates that there was nothing on that side in the library because it was cleaved close to the edge.

```{r}
cleavage_added_data = add_cleavages(joined_with_library,n_residues = 4)
